SPECS-decadal-MOS

### 2017-01-25 EU-Circle/eu-circle_case-study-5.Rmd
updated EU-Circle case study5

>>>>

Test to see if the long-wave outgoing radiation (OLR) can be used as a predictor for the winter-time wet-day mean precipitation over Germany. It contains information about cloud tops, and the hypothesis is that heavy precipitation comes from clouds with high (and cold) cloud tops.

```{r, fig.width=8, fig.height=8}
olr <- retrieve('~/Downloads/ERAINT-OLR-mon.nc', lon=c(-50,40),lat=c(40,70))
olr <- subset(as.4seasons(olr),it='djf')
eof.olr<- EOF(olr,n=5)
class(eof.olr)[3] <- "season"
mu.djf <- subset(as.4seasons(Y,FUN='wetmean'),it='djf')
pca.mu <- PCA(pcafill(mu.djf),n=5)
ds.mu.orl <- DS(pca.mu,eof.olr)
plot(ds.mu.orl,new=FALSE)
```

### 2017-01-25 SPECS/specs-decade-mos.Rmd
updated EU-Circle case study5

library(esd)
library(ncdf)
setwd("~/R")

@@

source("~/Dropbox/Public/SPECS/R/udg2esd_met.R") ## Upload udg2esd function

@@

```{r aggregate}
aggregatedailyfield <- function(fname,cline='cdo monmean',
                                output='mu_0.25deg_reg_v12.0.nc') {
  print('This function only works if you have CDO installed')
  print(paste(cline,fname,output))
  system(paste(cline,fname,output))
  x <- retrieve(output)
  invisible(x)
}

@@

```{r wetdaymean}
wetdaymean <- function(ifile,cline='cdo yearmean',fname='data/wetdaymean.nc') {
  print('calculate mask')
  system(paste('cdo gtc,1',ifile,'data/mask.nc'))
  ## her blir ofile en mask med 1 i alle tidsskritt med data over konstanten (satt til 0),
  ## og verdi 0 i alle andre
  print('apply mask')
  system(paste('cdo ifthen data/mask.nc',ifile, fname))
  ## her appliseres masken på ifile og lagres i ofile. (Øvrige punkter får verdien NA.)

  ##Disse går å kombinere til en rad:
  ##  print(paste('cdo ifthen -gtc,0',ifile,ifile,fname))
  ##  system(paste('cdo ifthen -gtc,0',ifile,ifile,fname))
  X <- aggregatedailyfield(fname=fname,cline=cline)
  Y <- aggregatedailyfield(fname=,'data/mask.nc',cline=cline,output='fw_0.25deg_reg_v12.0.nc')
  file.remove(fname); file.remove('data/mask.nc')
}

@@

print('Get the predictands: mu & fw from EOBS')
if (!file.exists('mu_0.25deg_reg_v12.0.nc'))
  mu.eobs <-  wetdaymean('data.ECAD/rr_0.25deg_reg_v12.0.nc') else
  mu.eobs <- retrieve('mu_0.25deg_reg_v12.0.nc')
fw.eobs <- retrieve('fw_0.25deg_reg_v12.0.nc')
attr(mu.eobs,'variable') <- 'mu'
attr(fw.eobs,'variable') <- 'fw'
attr(fw.eobs,'unit') <- 'fraction'
index(fw.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
index(mu.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))

>>>>

library(esd)
#library(ncdf)
setwd("~/R")

@@

source("/home/rasmusb/disk1/SPECS/R/udg2esd_met.R") ## Upload udg2esd function

@@

```{r aggregate}
aggregatedailyfield <- function(fname,cline='cdo monmean',
                                output='mu_0.25deg_reg.nc') {
  print('This function only works if you have CDO installed')
  print(paste(cline,fname,output))
  system(paste(cline,fname,output))
  x <- retrieve(output)
  invisible(x)
}

@@

```{r wetdaymean}
wetdaymean <- function(ifile,cline='cdo yearmean',fname='data/wetdaymean.nc') {
  print('calculate mask')
  system(paste('cdo gtc,1',ifile,'~/data/mask.nc'))
  ## her blir ofile en mask med 1 i alle tidsskritt med data over konstanten (satt til 0),
  ## og verdi 0 i alle andre
  print('apply mask')
  system(paste('cdo ifthen data/mask.nc',ifile, fname))
  ## her appliseres masken på ifile og lagres i ofile. (Øvrige punkter får verdien NA.)

  ##Disse går å kombinere til en rad:
  ##  print(paste('cdo ifthen -gtc,0',ifile,ifile,fname))
  ##  system(paste('cdo ifthen -gtc,0',ifile,ifile,fname))
  X <- aggregatedailyfield(fname=fname,cline=cline)
  Y <- aggregatedailyfield(fname=,'~/data/mask.nc',cline=cline,output='fw_0.25deg_reg.nc')
  file.remove(fname); file.remove('~/data/mask.nc')
}

@@

print('Get the predictands: mu & fw from EOBS')
if (!file.exists('~/data/mu_0.25deg_reg.nc'))
  mu.eobs <-  wetdaymean('~/data/data.ECAD/rr_0.25deg_reg.nc') else
  mu.eobs <- retrieve('~/data/mu_0.25deg_reg.nc')
fw.eobs <- retrieve('~/data/fw_0.25deg_reg.nc')
attr(mu.eobs,'variable') <- 'mu'
attr(fw.eobs,'variable') <- 'fw'
attr(fw.eobs,'unit') <- 'fraction'
index(fw.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
index(mu.eobs) <- year(as.Date(time,origin = as.Date("1950-01-01")))
